# Analyzing student data

*Describe the work you have done this week and summarize your learning.*

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using  

For this exercise I will be using dataset on Student's learning data collected by Kimmo Vehkalahti. I use smaller part of the data... 

The data set looks like this:
```{r}
library(GGally)
library(ggplot2)

learning2014 <- read.table("data/learning.csv", sep = ",", header = TRUE)
```

```{r}
str(learning2014)
summary(learning2014)
kuva <- ggpairs(learning2014, mapping = aes(col = gender, alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))
kuva
```
```{r}

```
And the graphical overview for the data looks like this:
```{r}
kuvaaja <- ggpairs(learning2014, mapping = aes(col = gender, alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))
kuvaaja
```