# Regression and model validation

*Describe the work you have done this week and summarize your learning.*

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using  

For this exercise I will be using dataset on Student's learning data collected by Kimmo Vehkalahti. I use smaller part of the data... 


```{r}
library(GGally)
library(ggplot2)

learning2014 <- read.table("data/learning.csv", sep = ",", header = TRUE)
learning2014$X <- NULL
```

##Data overview

In the first chunk I loaded the needed libraries and read csv data to a data frame. After that I used functions head(), str() and summary() to get a first look of the data.

The data set looks like this:

```{r}
head(learning2014)
```

```{r}
str(learning2014)
```

```{r}
summary(learning2014)
```
Data set has 166 observations and 7 variables. 3 variables are integers, 3 numericals and 1 variable is a factor with 2 levels.

Data consists of partipants' background information, their answers and exam points. 

Most of the participants were female. Their age was between 17 and 55 years, and the mean age of the participants was 25,51. 



```{r}

```
And the graphical overview for the data looks like this:
```{r}
kuvaaja <- ggpairs(learning2014, mapping = aes(col = gender, alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))
kuvaaja
```
There are some differences between male and female participants. Their age is